---
title: "Predicition Assignment"
author: "Prashant Sharma"
date: "24/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Loading training and test csv data files.
```{r}
training = read.csv("pml-training.csv",na.strings = c("", "NA"))
testing = read.csv("pml-testing.csv",na.strings = c("", "NA"))
dim(training)
dim(testing)
```

lets clean our dataset for NA entries.
```{r}
training <- training[ , colSums(is.na(training)) == 0]
training_set <- training[,-c(1:8)] #dropping irrelevant features
testing_set <- testing[,names(training_set[,-52])]
dim(training_set)
dim(testing_set)
```
Our task here is to classify or predict whether the dumb-bell curl done by the user is correct or not and what type of error he is doing that is in which class his exercise form belongs.

lets import few packages for our classification task.
```{r}
library(caret)
library(randomForest)
library(parallel)
library(doParallel)
```

```{r}
cluster <- makeCluster(detectCores() - 4)
registerDoParallel(cluster)
```

Before proceeding further lets create a validation set
```{r}
set.seed(1234)
intrain <- createDataPartition(training_set$classe , p = 0.75)[[1]]
new_training_set <- training_set[intrain,]


validation_set <- training_set[-intrain,]
dim(new_training_set)
dim(validation_set)

```


lets try Random forest. we will be applying cross validation method at 5 folds.

```{r}
fit_control<-trainControl(method = "cv" ,number = 5,allowParallel=TRUE)

model1 <- train(classe ~ . , method = "rf" ,trControl = fit_control, data = new_training_set, verbose = F )
```
```{r}
model1
```
Stopping the cluster.
```{r}
stopCluster(cluster)
registerDoSEQ()
```

Confusion Matrix
```{r}
prediction1 <- predict(model1 , newdata = validation_set)
confusionMatrix(prediction1 , as.factor(validation_set$classe))

```
Overall accuracy
```{r}
confusionMatrix(prediction1, as.factor(validation_set$classe))$overall[[1]]
```
Lets predict on our test set:
```{r}
prediction_test<- predict(model1 , newdata = testing)
prediction_test
```



