---
title: "Bootstrapping"
author: "Prashant Sharma"
date: "03/02/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Bootstrapping simulation

The app simulates bootstrapping procedure to infer the population mean and confidence interval.

## Instructions

- This app uses bootstrapping to infer mean and CI for the population.
- You can choose sample sizes and number of simulations from the sliders below.
- App is interactive so you will see the effect of various selections made by you.
- We are sampling from a random normal distribution with mean 25 , sd 5.
- You can toggle mean and CI by clicking on the checkboxes provided below.

## Internal calculation part 1

Drawing samples
```{r ,echo = TRUE,eval=FALSE}
n <- input$slider1
    b <- input$slider2
    resamples <- matrix(sample(population, n*b , replace= TRUE),b , n)
```

## Internal calculation part 2
calculating mean of means and confidence interval from the distribution of means.

```{r ,echo = TRUE,eval=FALSE }
means <- apply(resamples,1,mean)
    BS_mean <- mean(means)
    BS_quantile <- quantile(means , c(0.25,0.975))
    output$mean <- renderText({BS_mean})
    output$CI <- renderText({BS_quantile})
    output$Rmean <- renderText({25})
```

## Plotting.
plotting histogram of sampled means and drawing mean and CI lines.
```{r,echo = TRUE,eval=FALSE}
hist(means, col = "lightblue")
    if(input$mean){
      abline(v = BS_mean, col = "red", lw = 3)}
    if(input$CI){
      abline(v = BS_quantile, col = "blue",lw = 2)}
    

```

